|

### 2023-05-08 paper/01-introduction.Rmd
added figures to the data section

[I think we need a couple of paragraphs here to introduce the defensive linemen position, and the role/significance of linemen, why is it important to analyze them]

>>>>

[I think we need a couple of paragraphs here to introduce the defensive linemen position, and the role/significance of linemen (kinda similar to section 2 of rishav's paper https://arxiv.org/pdf/1906.11373.pdf)]

### 2023-05-08 paper/02-data.Rmd
added figures to the data section

We use the tracking data made available in the 2023 NFL BDB competition for our investigation. The data corresponds to 8557 passing plays across 122 games in the first eight weeks of the 2021 NFL regular season. The aforementioned NGS data provides the on-field location, speed, direction, and orientation of each player on the field (and the ball) at a rate of 10 Hz, along with event annotations (e.g., ball snapped, pass thrown, etc.). In this particular dataset, there are _INSERT NUMBER_ unique frames corresponding to moments of time from the start of the play at snap until the moment the quarterback either throws the pass or is sacked. (_VERIFY THIS STATEMENT MAKES SENSE_)

Table \ref{tab:track} displays example data for a play from the 2021 NFL regular season week six matchup between the Las Vegas Raiders and Denver Broncos, which ended with Broncos QB Teddy Bridgewater getting sacked by Raiders DE Maxx Crosby[^crosbysack]. _Figure X_ presents the locations of every Las Vegas (black) and Denver (orange) player on the field at four particular moments of time, with Maxx Crosby highlighted (blue).

\begin{table}
\caption{track. \label{tab:track}}
\centering
\begin{tabular}{rrrlrrrrrrrl}
\hline
frameId & jerseyNumber & team & x & y & s & a & dis & o & dir & event \\ 
\hline
7 & 98 & LV & 67.68 & 29.89 & 0.34 & 1.57 & 0.04 & 124.86 & 88.21 & ball\_snap \\ 
8 & 98 & LV & 67.76 & 29.89 & 0.69 & 2.13 & 0.08 & 124.07 & 89.59 & None \\ 
\vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots \\ 
50 & 98 & LV & 73.67 & 25.06 & 4.19 & 2.62 & 0.42 & 134.21 & 125.26 & qb\_sack \\ 
\hline
\end{tabular}
\end{table}

_INSERT FIGURE_

Along with the tracking information, the 2023 BDB includes scouting data provided by Pro Football Focus (PFF). PFF's scouting data includes manually collected player-level information at the play level, such as the player's role (e.g., if they are a pass rusher) and credited events (e.g., player is credited with hitting the QB on the play). In this manuscript, we use the PFF data to identify _INSERT NUMBER_ unique players designated in the "pass rush" role across all plays. For context, _Figure X_ displays the distribution of the number of observed pass rushers involved in a play, ranging from _INSERT NUMBER_ to _INSERT NUMBER_ with _INSERT NUMBER_ pass rushers as the most common value. We also leverage the PFF data to count how many hits, hurries, and sacks each pass rusher is credited with across span of collected data. Additionally, we use the PFF player roles to identify which players were labeled as blocking each pass rusher to adjust for opponent strength, as discussed in Section _INSERT NUMBER_.

INSERT FIGURE

(sample restriction)

We include only the frames between the ball snap and when a pass forward or QB sack is recorded for each play. We also remove all plays with multiple quarterbacks on the field, since we need a uniquely defined quarterback to calculate our measure. Using PFF scouting data, we only consider defenders with role "Pass rush" for evaluation.

>>>>

```{r eval = FALSE, echo = FALSE}
pass_rush <- read_csv(here("data", "pass_rush.csv.gz"))
pass_rush %>% select(gameId, playId, frameId) %>% n_distinct()
```

In the forthcoming analysis, we rely on the data from the 2023 NFL Big Data Bowl provided by the NFL Next Gen Stats tracking system.
The data corresponds to 8557 passing plays across 122 games in the first eight weeks of the 2021 NFL regular season. 
For each play, we have information on the on-field location, speed, angle, direction, and orientation of each player on the field and the football at a rate of 10 Hz, along with event annotations for each frame such as ball snap, pass forward, and quarterback sack, to name a few.
For our investigation, we consider only the frames between the ball snap and when a pass forward or quarterback sack is recorded for each play.
We also remove all plays with multiple quarterbacks on the field, since we need a uniquely defined quarterback to compute our metric.
After preprocessing, there are 251,060 unique frames corresponding to moments of time from the start of the play at snap until the moment the quarterback either throws the pass or is sacked.

Table \ref{tab:track} displays a tracking data example for a play from the 2021 NFL regular season week six matchup between the Las Vegas Raiders and Denver Broncos, which ended with Broncos QB Teddy Bridgewater getting sacked by Raiders DE Maxx Crosby[^crosbysack].
In addition, Figure \ref{fig:fig_field_raw} presents the locations of every Las Vegas (in black) and Denver (in orange) player on the field from this play at 1, 2, 3 and 4 seconds after the ball snap, with Maxx Crosby highlighted in blue.

\begin{table}
\caption{Example of tracking data for the play that resulted in a Maxx Crosby's sack. \label{tab:track}}
\centering
\begin{tabular}{ccccccccccc}
\hline
frameId & jerseyNumber & team & x & y & s & a & dis & o & dir & event \\ 
\hline
7 & 98 & LV & 67.68 & 29.89 & 0.34 & 1.57 & 0.04 & 124.86 & 88.21 & ball\_snap \\ 
8 & 98 & LV & 67.76 & 29.89 & 0.69 & 2.13 & 0.08 & 124.07 & 89.59 & None \\ 
\vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots \\ 
50 & 98 & LV & 73.67 & 25.06 & 4.19 & 2.62 & 0.42 & 134.21 & 125.26 & qb\_sack \\ 
\hline
\end{tabular}
\end{table}

```{r}
#| label: fig_field_raw
#| fig.cap: "A display of the player tracking data for a play during the Las Vegas Raiders (defense, in black) versus Denver Broncos (offense, in orange) NFL game on October 17, 2021. Raiders DE Maxx Crosby is highlighted in blue. Snapshots are captured at 1, 2, 3, and 4 seconds after the ball snap."
#| fig.width: 6.6
#| fig.height: 4.4
source(here("scripts", "11_fig_field_raw.R"))
fig_field_raw
```

Along with the tracking information, the 2023 BDB includes scouting data provided by Pro Football Focus (PFF). 
PFF's scouting data includes manually collected player-level information at the play level, such as the player's role (e.g., whether they are a pass rusher) and credited events (e.g., player is credited with hitting the QB on the play).
In this manuscript, we use the PFF data to identify 36,362 unique players designated in the "pass rush" role across all plays.
For context, Figure \ref{fig:pass_rushers_count} displays the distribution of the number of observed pass rushers involved in a play, ranging from 1 to 8 with 4 pass rushers as the most common value.
We also leverage the PFF data to count how many hits, hurries, and sacks each pass rusher is credited with across span of collected data. 
Additionally, we use the PFF player roles to identify which players were labeled as blocking each pass rusher to adjust for opponent strength, as discussed in Section \ref{sec:methods}.

```{r}
#| label: pass_rushers_count
#| fig.cap: "Distribution of the number of pass rushers in a play."
#| fig.width: 4.5
#| fig.height: 3
source(here("scripts", "12_fig_pass_rushers_count.R"))
pass_rushers_count
```
